Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-15 exp1/present2013.tex
remove classifying remove questions remove worthy result
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@682 43ef1190-90fd-4dd7-a769-d0121f02b80e

    \begin{itemize}
    \item When experimental economy is important,
    \item DoE theory offers extensive facilities for running a
      fraction of the runs ($2^{n-1}$ etc).
    \item The price is of smaller experiments is explanatory power.
    \end{itemize}
  \end{itemize}
\end{frame}

@@

Classifying factors:
  \begin{itemize}
  \item ``Range'' and ``Machine'' are called \emph{inactive factors}.
  \item ``BGPComp'', ``Lang'', ``Optional'', ``Union'' and ``TripleC''
    are called \emph{environmental factors}.
  \item ``Implement'' is called a \emph{control factor}.
  \end{itemize}

@@

\end{frame}
\note{  
  \begin{itemize}
  \item The paper shows how similar testing can be done to investigate
  when the new implementation fails.
\item The paper has two fractional factorial experiments.
  \item Should this simplistic experiment stand up to scrutiny?
  \end{itemize}
}

@@

\begin{frame}{Fractional experiment with more data}
\begin{figure}[ht!]
  \centerline{%
  \includegraphics[height=0.85\textheight,width=.9\textwidth]{frac64hugenormal.pdf}}
\end{figure}

@@

\section{Conclusion}

\begin{frame}
We saw
  \begin{itemize}
  \item ... an experimental setup using DoE.
  \item ... how the analysis pointed out the important effects.
  \item ... how we got a comprehensive view of the experiment.
  \item ... how hypothesis tests could be formulated.
  \item ... how 2-level experiments can determine significant effects,
    even though it is not good enough for modelling.
  \item ... how more economic experiments can be designed, and noted
    their limitations.
  \item ... finally how the experiment could be shown to be flawed.
  \end{itemize}
\end{frame}

\begin{frame}{Questions to ask}

\begin{enumerate}
\item Are there factors that cover all realistic features?
\item If not, are they adequately covered by randomization?
\item If so, would the variance resulting from randomization obscure
  factors that could provide clues that the levels are wrongly set?
\item By carefully examining interactions with ``Implement'', are
  there any that are unaccounted for, and that could point out wrongly
  set levels?
\end{enumerate}

\begin{frame}{What's a worthy result?}
  \begin{itemize}
  \item I have not made this a primary focus of my work.
  \item Even though I think I should.
  \item 3000 full-time researchers to construct the ATLAS experiment
    at CERN.
  \item Improvement in experimental methodology should be a worthy result.
  \end{itemize}

>>>>

    \begin{itemize}
    \item When experimental economy is important,
    \item DoE theory offers extensive facilities for running a
      fraction of the runs ($2^{n-1}$ etc).
    \item The price is of smaller experiments is explanatory power.
    \end{itemize}
  \end{itemize}
\end{frame}
\note{We first study a full factorial, in the paper we have three
  fractional, we shall see the final fractional}

@@

@@

\end{frame}
\note{  
  \begin{itemize}
  \item The paper shows how similar testing can be done to investigate
  when the new implementation fails.

  \item Should this simplistic experiment stand up to scrutiny?
  \end{itemize}
}

@@

\begin{frame}{Fractional experiment with more data}
\begin{figure}[ht!]
  \centerline{%
  \includegraphics[height=0.8\textheight,width=.9\textwidth]{frac64hugenormal.pdf}}
\end{figure}

@@

\begin{frame}{Conclusion}
We saw
  \begin{itemize}
  \item ... an experimental setup using DoE.
  \item ... how the analysis pointed out the important effects.
  \item ... how we got a comprehensive view of the experiment.
  \item ... how hypothesis tests could be formulated.
  \item ... how 2-level experiments can determine significant effects,
    even though it is not good enough for modelling.
  \item ... how more economic experiments can be designed, and noted
    their limitations.
  \item ... finally how the experiment could be shown to be flawed.
  \end{itemize}
\end{frame}
